SUPPLEMENTARY INFORMATION: NMRlipids Databank: Overlay Databank of Lipid Membrane Simulations Arising from Open Collaboration

### 2022-10-05 SI.tex
Updates from Overleaf
Add figure to SI and update pdf

\documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{tablefootnote}

@@

@@

\begin{figure}[!h]
    \centerfloat
    \includegraphics[width = 180mm]{Figures/QualityCorrelationsSI.pdf}
    \caption{Dependence of form factor, electron density profiles along membrane normal, and C-H bond orderparameters (from top to bottom) on simulation box size with different cholesterol concentration. }
    \label{fig:sizedependence}
\end{figure}

@@

\begin{figure}[!h]
    \centerfloat
    \includegraphics[width = 240mm]{Figures/SizeDependence.pdf}
    \caption{Dependence of form factor, electron density profiles along membrane normal, and C-H bond orderparameters (from top to bottom) on simulation box size with different cholesterol concentration. }
    \label{fig:sizedependence}
\end{figure}

>>>>

\documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{tablefootnote}
\usepackage{xr}

@@

\makeatletter
\newcommand*{\addFileDependency}[1]{% argument=file name and extension
  \typeout{(#1)}
  \@addtofilelist{#1}
  \IfFileExists{#1}{}{\typeout{No file #1.}}
}
\makeatother

\newcommand*{\myexternaldocument}[1]{%
    \externaldocument{#1}%
    \addFileDependency{#1.tex}%
    \addFileDependency{#1.aux}%
}

\myexternaldocument{main}

\renewcommand{\thetable}{S\arabic{table}}%
\renewcommand{\thefigure}{S\arabic{figure}}%
\renewcommand{\thesection}{S\arabic{section}}%
\renewcommand{\thepage}{S\arabic{page}}%

@@

\begin{figure}[!h]
    \centerfloat
    \includegraphics[width = 180mm]{Figures/QualityCorrelationsSI.pdf}
    \caption{Dependence of form factor, electron density profiles along membrane normal, and C-H bond orderparameters (from top to bottom) on simulation box size with different cholesterol concentration. }
    \label{fig:QualityCorrelationsSI}
\end{figure}

@@

\begin{figure}[!h]
    \centerfloat
    \includegraphics[width = 240mm]{Figures/SizeDependence.pdf}
    \caption{Dependence of form factor, electron density profiles along membrane normal, and C-H bond orderparameters (from top to bottom) on simulation box size with different cholesterol concentration. Simulations with 64, 256 or 1024 POPC lipids taken from Ref.~\citenum{javanainen_matti_2021_7035350}. }
    \label{fig:sizedependence}
\end{figure}

\pagebreak
\section{Finding the best models for PC and PE mixtures}

\begin{figure}[!h]
    \centering
    \includegraphics[width = 140mm]{Figures/POPC_POPE_dataSI.pdf}
    \caption{Simulations with the data for both POPC (top) and POPE (bottom) directly compared with the experimental data.
      The area per lipid in simulations increase from left to right.
      Simulations with the best overall quality for POPC and POPE order parameters are circled by a square.
  }
    \label{fig:POPC_POPE_dataSI}
\end{figure}
